\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Lin Fu (Flynn)} % Your name
\address{Email: flynn.fu@zenithz.io}
\address{Tel: (+61) 420 231 948}
\address{Homepage: zenithz.io}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Career Objective}
 I am passionate to work with a great team on challenging problems which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.
\end{rSection}

\begin{rSection}{Education}
\\{\bf The University of Sydney, Australia} \hfill {\em Mar 2017 - Mar 2021(Expected)}
\\ \textit{ Bachelor of Computer Science and Technology (Honours)} 
\\  Computer Science, Information Systems\\ 
\\{\bf Auckland Grammar School, New Zealand} \hfill {\em Feb 2014 - Mar 2017} 
\\  Multiple courses related to business studies, accounting and economics. \hfill { Overall: Merit } 

\end{rSection}

%--------------------------------------------------------------------------------
%    Projects
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}
{\bf Sepsis UX, NSW Pathology}
\\ The project aims to embark on UX development work, designing interface for a new application for clinicians, that uses real-time data collected from NSWHP Point of Care testing devices to support a sepsis pathway. The project is developed using Angular and it can be found on my website.\\
\\ {\bf Pens Up, The University of Sydney}
\\ The project aims to develop an application to help elementary and primary school students improve on their hand writing skills. The project is developed using Unity and the GitHub link can be found on my website.\\ 
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Work Experience}

\begin{rSubsection}
{NSW Health Pathdology, Sydney}{Jan 2020 - Present}{PoCT Customer & Product Support Officer}{Westmead Hosipital}
\\ On-site and remote full time under NSW Pathology. Responsibilities are continuously integrating the tool created in the project section, data collections within the emergency department and collecting feedback from the nursing staff in order to improve the design and usability of the tool.\\ 
\end{rSubsection}
\begin{rSubsection}
{The University of Sydney, Sydney}{Jul 2019 - Dec 2019}{Academic Tutor}{Human Computer Interaction}
\\ Been tutoring for a third-year university Human-computer interaction course. Was responsible to bridge the gap between the students and the lecturer while guiding students through additional materials and their assignments. Was also involved in assignment marking, exam marking and data entries for the course.\\ 
\end{rSubsection}
\pagebreak
\begin{rSubsection}
{61 Games, Shenzhen}{Dec 2016 - Feb 2017}{Tester}{}
\\ Two-month internship with mobile game developing company 61 games, focusing on testing alpha version of games identifying bugs and possible income spots and providing reports on a frequent basis.\\ 
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Volunteering EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Volunteer Experience}
\begin{rSubsection}
{The University of Sydney, Sydney}{Jul 2018 – Dec 2018}{Academic Mentor}{Introduction To Programming, Object-Oriented Programming}
\\ Been mentoring first-year university students on first-year programming courses. Responsibility was majorly bridging the gap between the students and the lecturer and tutor, actively communicate with students and provide additional help beyond the tutor making sure that they understand the course content.\\ 
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Cirrucular} \itemsep -3pt
\item Worked for a tutoring company as a private tutor for multiple university academic courses since 2018.
\item Being the Head Bartender in a top50 restaurant(Nanam) in Auckland, New Zealand.
\item Involved in Microsoft Coding Competition 2018.
\item Involved in UNI-HACK Sydney 2018.
\item Achieved A (99.08\%) in an introductory course to Python at Harvard Summer School.

\end{rSection}

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
\begin{rSection}{Personal Traits}
\item Highly motivated and eager to learn new things.
\item Ability to work as an individual as well as in group.
\item Good at communicating and able to fit in quickly with changing environments and situations .
\item Able to effectively manage task while multitasking, going fast while assuring quality.
\end{rSection}

%----------------------------------------------------------------------------------------
% Technical Skills
%----------------------------------------------------------------------------------------
\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Usability and Design \ & Basamiq, AdobeXD \\ 
Back-end Skills \ & Python, Java, C++, R, SQL, C, Lisp \\ 
Front-end Skills \ & NodeJS, Angular, Vue, Html, CSS \\ 
Git \ & GitHub, Bit-bucket\\  
Project management and Change management Skills\\ 
Finance Skills \ & CFA Level 1\\  
Additional Tools & Excel, Latex \\
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
% Professional Referees
%----------------------------------------------------------------------------------------
\begin{rSection}{Professional Referees}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Dr Anusha Withana (Lecturer, Sydney University) \ & Email: anusha.withana@syndey.edu.au\\
Ariel Herbert-Voss (PhD, Harvard University) \ & Email: ariel.herbertvoss@gmail.com \\
\end{tabular}

\end{rSection}

\end{document}
